Report

### 2021-07-05 Rmd/report.Rmd
Better comments, compare CHILDES vs. SUBTLEX frequencies.

# load packages
library(papaja)
library(knitr)
library(tidyverse)
library(bilingualr)
library(lubridate)
library(scales)
library(DiagrammeR)
library(janitor)
library(lme4)
library(broom.mixed)
library(gt)
library(patchwork)
library(htmltools)
library(shiny)
library(here)

@@

```{r participants_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	ggplot(aes(lp, fill = as.factor(test_language))) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	labs(x = "Group", y = "Sample size", fill = "Test language") +
	theme(
		legend.position = "top",
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) +
	ggsave(here("Figures", "sample.png"))

@@

```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, out.width="100%"}
# plot participants
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>%
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		),
		age_group = str_remove(age_group, " months")
	) %>%
	drop_na(valid_status) %>% 
	ggplot(aes(age_group, participant, colour = valid_status)) +
	facet_grid(location~lp, scales = "free") +
	geom_line(aes(group = interaction(lp, participant))) +
	geom_point(size = 2) +
	geom_hline(yintercept = 0.2, linetype = "dashed") +
	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Validity status") +
	theme(
		legend.position = "right",
		legend.title = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_blank(),
		axis.text.y = element_blank(),
		axis.ticks.y = element_blank()
	) +
	ggsave(here("Figures", "cohort.png"))
```

@@

```{r stimuli_frequency_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	ggplot(aes(trial_type, frequency_prime, colour = trial_type, fill = trial_type)) +
	facet_wrap(location~test_language) +
	geom_violin() +
	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
	geom_jitter(colour = "black", size = 1, shape = 1,
				width = 0.1, alpha = 0.5, stroke = 1) +
	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
		 colour = "Trial type", fill = "Trial type") +
	theme(
		legend.position = "none",
		legend.title = element_blank(),
		axis.text = element_text(size = 9),
		axis.title.x = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		plot.caption = element_text(size = 10, hjust = 0),
	)

@@

```{r stimuli_frequency_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	ggplot(aes(trial_type, frequency_target, colour = trial_type, fill = trial_type)) +
	facet_wrap(location~test_language) +
	geom_violin() +
	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
	geom_jitter(colour = "black", size = 1, shape = 1,
				width = 0.1, alpha = 0.5, stroke = 1) +
	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
		 colour = "Trial type", fill = "Trial type") +
	theme(
		legend.position = "none",
		legend.title = element_blank(),
		axis.text = element_text(size = 9),
		axis.title.x = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		plot.caption = element_text(size = 10, hjust = 0),
	)
```

@@

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	drop_na() %>% 
	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime), xmin = familiarity_ci_lower_prime, xmax = familiarity_ci_upper_prime, colour = trial_type, fill = trial_type)) +
	facet_wrap(~test_language, scales = "free_y") +
	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	geom_vline(data = means, aes(xintercept = familiarity_prime, colour = trial_type), size = 1) +
	geom_errorbar() +
	geom_point() +
	labs(x = "% of infants that understand", y = "Prime word",
		 colour = "Trial type", fill = "Trial type") +
	scale_x_continuous(labels = scales::percent) +
	theme_custom() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
	)

@@

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	drop_na() %>% 
	ggplot(aes(familiarity_target, reorder(target, familiarity_target), xmin = familiarity_ci_lower_target, xmax = familiarity_ci_upper_target, colour = trial_type, fill = trial_type)) +
	facet_wrap(~test_language, scales = "free_y") +
	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	geom_vline(data = means, aes(xintercept = familiarity_target, colour = trial_type), size = 1) +
	geom_errorbar() +
	geom_point() +
	labs(x = "% of infants that understand", y = "Target word",
		 colour = "Trial type", fill = "Trial type") +
	scale_x_continuous(labels = scales::percent) +
	theme_custom() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
	)

@@

animacy %>% 
	filter(role=="Prime") %>% 
	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
	facet_wrap(role~location~test_language, ncol = 4) +
	geom_col(position = position_fill(), colour = "white") +
	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	labs(title = "Prime", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
	scale_y_continuous(labels = scales::percent) +
	coord_flip() + 
	theme(
		axis.title.x = element_blank()
	) +

	animacy %>% 
	filter(role=="Target") %>% 
	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
	facet_wrap(role~location~test_language, ncol = 4) +
	geom_col(position = position_fill(), colour = "white") +
	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
	scale_y_continuous(labels = scales::percent) +
	coord_flip() +

@@

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	pivot_longer(c(category_prime, category_target), names_to = "role", values_to = "category") %>% 
	mutate(role = str_to_sentence(str_remove(role, "_category"))) %>% 
	drop_na() %>% 
	count(trial_type, test_language, location, role, category) %>% 
	ggplot(aes(n, trial_type, colour = category, fill = category, order = n)) +
	facet_grid(role~location~test_language) +
	geom_col(position = position_fill()) +
	labs(x = "% of trials", y = "Trial type",
		 colour = "Trial type", fill = "Trial type") +
	scale_fill_manual(values = wesanderson::wes_palette(name = "Zissou1", n = 9, type = "continuous")) +
	scale_colour_manual(values = wesanderson::wes_palette(name = "Zissou1", n = 9, type = "continuous")) +
	scale_x_continuous(labels = scales::percent) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text = element_text(size = 9),
		axis.title.y = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
	)

@@

VarCorr(fit)$participant %>% 
	cov2cor() %>% 
	as.data.frame() %>% 
	rownames_to_column("term1") %>% 
	gt(rowname_col = "term1") %>% 
	fmt_number(columns = 2:9) %>% 
	data_color(
		columns = 2:9,
		colors = scales::col_numeric(
			palette = RColorBrewer::brewer.pal(n = 9, name = "Oranges"),
			domain = c(-1, 1), alpha = 0.5
		)
	)

@@

augment(fit) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 caption = "Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups. Sample sizes are indicated at the upper left corner in each panel. The first and last 300 ms in each trial\nwere trimmed before the analysis.") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme_custom() +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7),
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	) +
	ggsave(here("Figures", "emmeans.png"), height = 6)
```

@@

```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>%
	left_join(vocab) %>% 
	drop_na(valid_participant) %>% 
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		)
	) %>% 
	ggplot(aes(lp, fill = valid_status)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	scale_colour_brewer(palette = "Set1") +
	labs(x = "Group", y = "Sample size", fill = "Valid?") +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) +
	ggsave(here("Figures", "participants_attrition.png"))
```

@@

```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants, participant, location)) %>% 
	count(location, lp, age_group, trial_type, valid_status) %>% 
	drop_na(trial_type) %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill()) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	scale_y_continuous(labels = scales::percent) +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

@@

```{r attirion_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime)) %>% 
	drop_na(trial_type, frequency_prime) %>% 
	mutate(frequency_prime = round(frequency_prime)) %>% 
	count(trial_type, age_group, valid_status, trial_type, frequency_prime) %>% 
	ggplot(aes(as.factor(frequency_prime), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = scales::percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

@@

```{r attrition_frequency_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target)) %>% 
	drop_na(trial_type, frequency_target) %>% 
	mutate(frequency_target = round(frequency_target)) %>% 
	count(trial_type, age_group, valid_status, trial_type, frequency_target) %>% 
	ggplot(aes(as.factor(frequency_target), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = scales::percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

>>>>

# load packages
library(papaja)
library(knitr)
library(tidyverse)
library(lubridate)
library(scales)
library(DiagrammeR)
library(janitor)
library(lme4)
library(broom.mixed)
library(gt)
library(patchwork)
library(htmltools)
library(wesanderson)
library(shiny)
library(here)

@@

```{r participants_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	ggplot(aes(lp, fill = as.factor(test_language))) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	labs(x = "Group", y = "Sample size", fill = "Test language") +
	theme(
		legend.position = "top",
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) 
```

@@

```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, out.width="100%"}
# plot participants
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>%
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		),
		age_group = str_remove(age_group, " months")
	) %>%
	drop_na(valid_status) %>% 
	ggplot(aes(age_group, participant, colour = valid_status)) +
	facet_grid(location~lp, scales = "free") +
	geom_line(aes(group = interaction(lp, participant))) +
	geom_point(size = 2) +
	geom_hline(yintercept = 0.2, linetype = "dashed") +
	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Validity status") +
	theme(
		legend.position = "right",
		legend.title = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_blank(),
		axis.text.y = element_blank(),
		axis.ticks.y = element_blank()
	)
```

@@

#### CHILDES vs. SUBTLEX

```{r frequencies_compare, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

frequency_compare_data <- bind_rows(
	stimuli %>%
		distinct(test_language, prime, .keep_all = TRUE) %>%
		select(prime, test_language, matches("frequency_prime")) %>% 
		rename(word = prime, frequency_subtlex = frequency_prime_subtlex,
			   frequency_childes = frequency_prime_childes),
	stimuli %>%
		distinct(test_language, target, .keep_all = TRUE) %>%
		select(target, test_language, matches("frequency_target")) %>% 
		rename(word = target, frequency_subtlex = frequency_target_subtlex,
			   frequency_childes = frequency_target_childes),
) %>% 
	group_by(test_language) %>% 
	mutate_at(vars(starts_with("frequency")), function(x) scale(x)[,1])

frequency_compare_test <- group_split(frequency_compare_data) %>% 
	set_names(c("Catalan", "English", "Spanish")) %>% 
	map(function(x) {
		a <- pull(x, frequency_subtlex)
		b <- pull(x, frequency_childes)
		tidy(cor.test(a, b), use = "complete.obs")
	}) %>% 
	bind_rows(.id = "test_language") %>% 
	clean_names()

@@

We tested the correlation between the (standardised) lexical frequencies of the stimuli extract from SUBTLEX (adult norms based on subtitles) and CHILDES (child norms based on audio transcriptions) within each test language using a Pearson's product-moment correlation at .05 confidence level (two-sided):

```{r stimuli_frequency_compare_test, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

frequency_compare_test %>% 
	select(test_language, estimate, statistic, parameter, p_value, conf_low, conf_high) %>% 
	mutate(p_value = printp(p_value)) %>% 
	gt(rowname_col = "test_language") %>% 
	fmt_number(c(2, 3, 6, 7), decimals = 2) %>% 
	cols_merge(c("conf_low", "conf_high"), pattern = "{1}, {2}") %>% 
	cols_label(
		estimate = md("**Correlation**"),
		statistic = md("***t***"),
		parameter = md("***df***"),
		p_value = md("***p***"),
		conf_low = md("**CI<sub>95%<sub/>**")
	)

```{r stimuli_frequency_compare_plot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}

frequency_compare_data %>% 
	ggplot(aes(frequency_subtlex, frequency_childes, colour = test_language, fill = test_language)) +
	facet_wrap(~test_language) +
	geom_point(alpha = 0.5, stroke = 1, shape = 1) +
	geom_smooth(method = "lm") +
	labs(x = "SUBTLEX (adult norms)", y = "CHILDES (child norms)",
		 colour = "Language", fill = "Language") +
	coord_fixed() +
	theme(
		legend.position = "none",
		legend.title = element_blank(),
		axis.text = element_text(size = 9),
		axis.title.x = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		plot.caption = element_text(size = 10, hjust = 0),
	)

#### CHILDES {.tabset .tab-pills}

##### Prime

```{r stimuli_frequency_childes_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	ggplot(aes(trial_type, frequency_prime_childes, colour = trial_type, fill = trial_type)) +
	facet_wrap(location~test_language) +
	geom_violin() +
	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
	geom_jitter(colour = "black", size = 1, shape = 1,
				width = 0.1, alpha = 0.5, stroke = 1) +
	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
		 colour = "Trial type", fill = "Trial type") +
	theme(
		legend.position = "none",
		legend.title = element_blank(),
		axis.text = element_text(size = 9),
		axis.title.x = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		plot.caption = element_text(size = 10, hjust = 0),
	)

##### Target

```{r stimuli_frequency_childes_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	ggplot(aes(trial_type, frequency_target_childes, colour = trial_type, fill = trial_type)) +
	facet_wrap(location~test_language) +
	geom_violin() +
	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
	geom_jitter(colour = "black", size = 1, shape = 1,
				width = 0.1, alpha = 0.5, stroke = 1) +
	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
		 colour = "Trial type", fill = "Trial type") +
	theme(
		legend.position = "none",
		legend.title = element_blank(),
		axis.text = element_text(size = 9),
		axis.title.x = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		plot.caption = element_text(size = 10, hjust = 0),
	)
```

##### {-}

#### SUBTLEX {.tabset .tab-pills}

##### Prime

```{r stimuli_frequency_subtlex_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	ggplot(aes(trial_type, frequency_prime_subtlex, colour = trial_type, fill = trial_type)) +
	facet_wrap(location~test_language) +
	geom_violin() +
	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
	geom_jitter(colour = "black", size = 1, shape = 1,
				width = 0.1, alpha = 0.5, stroke = 1) +
	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
		 colour = "Trial type", fill = "Trial type") +
	theme(
		legend.position = "none",
		legend.title = element_blank(),
		axis.text = element_text(size = 9),
		axis.title.x = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		plot.caption = element_text(size = 10, hjust = 0),
	)

##### Target

```{r stimuli_frequency_subtlex_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	ggplot(aes(trial_type, frequency_target_subtlex, colour = trial_type, fill = trial_type)) +
	facet_wrap(location~test_language) +
	geom_violin() +
	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
	geom_jitter(colour = "black", size = 1, shape = 1,
				width = 0.1, alpha = 0.5, stroke = 1) +
	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
		 colour = "Trial type", fill = "Trial type") +
	theme(
		legend.position = "none",
		legend.title = element_blank(),
		axis.text = element_text(size = 9),
		axis.title.x = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		plot.caption = element_text(size = 10, hjust = 0),
	)
```

##### {-}

@@

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	drop_na() %>% 
	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime), xmin = familiarity_ci_lower_prime, xmax = familiarity_ci_upper_prime, colour = trial_type, fill = trial_type)) +
	facet_wrap(~test_language, scales = "free_y") +
	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	geom_vline(data = means, aes(xintercept = familiarity_prime, colour = trial_type), size = 1) +
	geom_errorbar() +
	geom_point() +
	labs(x = "% of infants that understand", y = "Prime word",
		 colour = "Trial type", fill = "Trial type") +
	scale_x_continuous(labels = percent) +
	theme_custom() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
	)

@@

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	drop_na() %>% 
	ggplot(aes(familiarity_target, reorder(target, familiarity_target), xmin = familiarity_ci_lower_target, xmax = familiarity_ci_upper_target, colour = trial_type, fill = trial_type)) +
	facet_wrap(~test_language, scales = "free_y") +
	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	geom_vline(data = means, aes(xintercept = familiarity_target, colour = trial_type), size = 1) +
	geom_errorbar() +
	geom_point() +
	labs(x = "% of infants that understand", y = "Target word",
		 colour = "Trial type", fill = "Trial type") +
	scale_x_continuous(labels = percent) +
	theme_custom() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
	)

@@

animacy %>% 
	filter(role=="Prime") %>% 
	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
	facet_wrap(role~location~test_language, ncol = 4) +
	geom_col(position = position_fill(), colour = "white") +
	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	labs(title = "Prime", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
	scale_y_continuous(labels = percent) +
	coord_flip() + 
	theme(
		axis.title.x = element_blank()
	) +

	animacy %>% 
	filter(role=="Target") %>% 
	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
	facet_wrap(role~location~test_language, ncol = 4) +
	geom_col(position = position_fill(), colour = "white") +
	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
	scale_y_continuous(labels = percent) +
	coord_flip() +

@@

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	pivot_longer(c(category_prime, category_target), names_to = "role", values_to = "category") %>% 
	mutate(role = str_to_sentence(str_remove(role, "_category"))) %>% 
	drop_na() %>% 
	count(trial_type, test_language, location, role, category) %>% 
	ggplot(aes(n, trial_type, colour = category, fill = category, order = n)) +
	facet_grid(role~location~test_language) +
	geom_col(position = position_fill()) +
	labs(x = "% of trials", y = "Trial type",
		 colour = "Trial type", fill = "Trial type") +
	scale_fill_manual(values = wes_palette(name = "Zissou1", n = 9, type = "continuous")) +
	scale_colour_manual(values = wes_palette(name = "Zissou1", n = 9, type = "continuous")) +
	scale_x_continuous(labels = percent) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text = element_text(size = 9),
		axis.title.y = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
	)

@@

VarCorr(fit)$participant %>% 
	cov2cor() %>% 
	as.data.frame() %>% 
	rownames_to_column("term1") %>% 
	gt(rowname_col = "term1") %>% 
	fmt_number(columns = 2:9) %>% 
	data_color(
		columns = 2:9,
		colors = col_numeric(
			palette = RColorBrewer::brewer.pal(n = 9, name = "Oranges"),
			domain = c(-1, 1), alpha = 0.5
		)
	)

@@

augment(fit) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 caption = "Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups. Sample sizes are indicated at the upper left corner in each panel. The first and last 300 ms in each trial\nwere trimmed before the analysis.") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme_custom() +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7),
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	) 
```

@@

```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>%
	left_join(vocab) %>% 
	drop_na(valid_participant) %>% 
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		)
	) %>% 
	ggplot(aes(lp, fill = valid_status)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	scale_colour_brewer(palette = "Set1") +
	labs(x = "Group", y = "Sample size", fill = "Valid?") +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) 
```

@@

```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants, participant, location)) %>% 
	count(location, lp, age_group, trial_type, valid_status) %>% 
	drop_na(trial_type) %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill()) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	scale_y_continuous(labels = percent) +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

@@

```{r attirion_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
	drop_na(trial_type, frequency_prime_childes) %>% 
	mutate(frequency_prime_childes = round(frequency_prime_childes)) %>% 
	count(trial_type, age_group, valid_status, trial_type, frequency_prime_childes) %>% 
	ggplot(aes(as.factor(frequency_prime_childes), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

@@

```{r attrition_frequency_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
	drop_na(trial_type, frequency_target_childes) %>% 
	mutate(frequency_target_childes = round(frequency_target_childes)) %>% 
	count(trial_type, age_group, valid_status, trial_type, frequency_target_childes) %>% 
	ggplot(aes(as.factor(frequency_target_childes), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```
